What lab space, testing grounds, makerspaces, etc. will you need to complete the project? Will you require any specific equipment, and if so, where will you get it (borrow, lease, purchase, outsource, already present in the lab, etc.). This section should occupy 1/2 page.

Since we are currently facing an unusual situation in the COVID-19 pandemic, we will be conducting lab experiments and building equipment at a place where not many people present. Facilities can be either home or UTA CSE Senior Design lab. 

Facilities has to have enough space to work on equipment, a power supply, and a table with a flat surface. Requirements for the facilities will be either leased or already present in the lab. 

Required materials for the equipment for this project are three containers; one for a hot liquor tank, the other for a mash tun, and another for a storage kettle. Three pumps will be used to push the liquid in tanks to other tanks when the environment in tanks meets a certain condition. A heater is used in the hot liquor tank to keep the water at a certain temperature. A coil gets water from the mash tun when the temperate of the water in the mash tun drops below the targeted temperature and heats up the water for a certain temperature. A thermometer reading water temperature in a hot liquor tank, a timer for brewing time, and relays controlling the heater, pumps, and reading temperature sensor will be purchased or borrowed from UTA. 

An application and a website will be created to provide an interface between users and the brewing system. Online database, the domain name for the website will be purchased.
