An in-depth explanation of the problem, including the "business case". What is wrong with the status-quo or what opportunity exists that justifies undertaking this project (expanding upon the problem statement)? If you have a clear customer or sponsor, why do they want you to work on this? What is the existing relationship, if any, between the development team and the customer? This section should occupy 1/2 - 1 full page.

\vspace{5mm}

The process of brewing can be something that is very easy to make mistakes on, espcially as a beginner. The idea of this project is to make it to where even the biggest laymen can accomplish a decent tasting beer.


\vspace{5mm}

A typical brewing day involves monitoring and keeping a hot liquor tank (HLT) at a desired temperature, then the
brewer has to send the hot water from the HLT to the empty mash tun for pre-heating. After a set amount of time, the water from the mash tun
will be sent back to the HLT to make sure the mash tun is at the desired temperature. While in the process of
pre-heating, the HLT has to be monitored and will be continuously heated up to the desired temperature. The next step is to start
the mash by mixing in the grain with the hot water inside the mash tun. The water inside the mash tun must be kept at a specific
temperature for a set amount of time. If the water drops below the desired temperature, a pump is turned on and the water
is sent through a pump to a coil inside the HLT to heat the water. Once the desired amount of time has passed, the HLT will
be heated up to a higher temperature and then sent to the mash tun to rinse the sugars.
At the same time, beer inside the mash tun will be pumped into the boil kettle.
Once all the beer has been sent to the boil kettle, the brewer has the boil the beer and set a timer to add hops to the beer
after each cycle. Once the boil is finished, the beer inside the boil kettle will be sent through a chiller to the fermenter.