This is the "What" of the project and it states what will be done to address the problem statement. This section should focus mostly on what your solution is going to be and what it is going to do (i.e., we are going to build an app, robot, device, etc. to perform some task which mitigates the problem). If someone were to ask you \textit{"What are you doing for your senior design project?"}, this is section is basically what you would tell them.


\vspace{5mm}

Our goal is to be able to plug a recipe into a web application, that will tell the sensors, heat source, and pumps exactly how to produce the beer. 

\vspace{5mm}

Our project will simplify the brewers job by heating and pumping the water to the containers through automation. This will
ensure the water is kept at the desired temperature throughout the whole process and will help the brewer monitor all
parts of the brewing process without requiring them to manually reheat/distribute the water. Automation will be done through the use of heat sensors, pumps, and microcontrollers that will communicate to a web-app/phone app.
The brewer will be able to
control the what temperatures the water will be set to and the amount of time they would like to spend on any step of the brewing process.

\begin{itemize}
  
  \item put together sensors into something that can interface with a web server
  \item interface with the sensors through a web portal of some kind
  \item program the sensor to complete recipe specifications
  \item to control the heating coils to positively impact the beer
  \item the variables that concern
   
  \item wait and monitor, upon completion enjoy beer

\end{itemize}